Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-31 CJM/Geometric types to CJM v3.tex
Record keeping

\begin{abstract}
We show that the types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable, subject to a mild hypothesis.
To do this we must find the function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
In previous work we considered the case of commutative smooth group schemes and found that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  
In this paper we give a modification of the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.  
We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu.
We combine these sheaves with Lusztig's character sheaves on reductive algebraic groups over finite fields and the geometrization of the Weil representation found by Gurevich and Hadani, to define \emph{geometric types} for supercuspidal representations of tamely ramified $p$-adic groups.
\end{abstract}

>>>>

\begin{abstract}
We show that the types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable, subject to a hypothesis.
To do this we must find the function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
In previous work we considered the case of commutative smooth group schemes and found that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  
In this paper we give a modification of the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.  
We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu.
We combine these sheaves with Lusztig's character sheaves on reductive algebraic groups over finite fields and the geometrization of the Weil representation found by Gurevich and Hadani, to define \emph{geometric types} for supercuspidal representations of tamely ramified $p$-adic groups.
\end{abstract}

### 2017-08-31 CJM/second letter to CJM.tex
Record keeping

\noindent{Dear Isolde Prince,}
\medskip

@@

\begin{enumerate}[label=(\roman*)]
\item We have fixed the typo.
\item The reviewer is correct that we do not need smoothness.
\item We have changed all the $i$s to $j$s.
\item We have changed $\cs{L}$ to $(\cs{L}, \mu)$ as suggested.
\item We have added the adjective ``linear'' at various points throughout the paper, including this one.
\item We have added a note as suggested.
\item We couldn't find a way to clarify this without adding a lot of extra material, which we thought would actually hurt the clarify of the exposition.  We therefore left these statements unchanged.
\end{enumerate}

>>>>

\noindent{Dear Professors Goren and Addario-Berry,}
\medskip

@@

\begin{enumerate}[label=(\roman*)]
\item We have fixed the typo.
\item The reviewer is correct that we do not need smoothness.
\item We have changed all the $i$s to $j$s.
\item We have changed $\cs{L}$ to $(\cs{L}, \mu)$ as suggested.
\item We have added the adjective ``linear'' at various points throughout the paper, including this one.
\item We have added a note as suggested.
\item We couldn't find a way to clarify this without adding a lot of extra material, which we thought would actually detract from the exposition.  We therefore left these statements unchanged.
\end{enumerate}
